Science Drivers for LSST Alert Distribution Latency

### 2020-02-28 draft-latency.tex
updates

\setDocAbstract{%
\textcolor{red}{\bf EXTREME DRAFT. DO NOT CITE OR READ.}\\
A gathering place for the science drivers related to alert packet distribution latency.
}

@@

Increasing the alert latency \emph{might} enable the stream to be delivered to more brokers, thereby increasing the amount of alerts-related science done by the community.
Or it might allow human and computational resources that are currently dedicated to building a DMS which can deliver a 1 minute latency to be repurposed. 
\textbf{There is currently no tabled proposal to increase the alert latency from 60 seconds}, but in case there ever is, this document collects the science drivers for short timescale alert distribution.
\textbf{Time-domain astronomy remains a rapidly evolving field and this should be considered a living, in-progress document}.

>>>>

\setDocAbstract{%
\textcolor{red}{\bf EXTREME DRAFT. DO NOT CITE OR READ.}\\
A gathering place for the science drivers related to alert packet distribution latency.
\textcolor{red}{\textbf{There is currently no tabled proposal to change the alert latency from 60 seconds}}, but in case there ever is, this document collects the science drivers for short timescale alert distribution.}

@@

Increasing the alert latency \emph{might} enable the stream to be delivered to more brokers, thereby increasing the amount of alerts-related science done by the community.
Or it might allow human and computational resources that are currently dedicated to building a DMS which can deliver a 1 minute latency to be repurposed. 
\textcolor{red}{\textbf{There is currently no tabled proposal to increase the alert latency from 60 seconds}}, but in case there ever is, this document collects the science drivers for short timescale alert distribution.
\textbf{Time-domain astronomy remains a rapidly evolving field and this should be considered a living, in-progress document}.
